Verification of Stencil Computations through Spatial Specifications

### 2016-07-06 paper.tex
putting the inequations back
putting back lots of stuff that was somehow lost

Figure~\ref{fig:equations} lists the equational theory for
specifications which is defined by the binary relation $\equiv$
between region terms. Stencil declarations are considered
equal when they have the same modifiers and $\equiv$ equates
their regions, \ie{}:
\begin{align*}
(\textit{region} \equiv \textit{region'}) 
 \Rightarrow \quad\;\; & \texttt{stencil} \; [\textit{approx},] \; [\textit{mult},] \;
\textit{region} \\[-0.4em]
\quad \equiv \; & \texttt{stencil} \; [\textit{approx},] \;
            [\textit{mult},] \; \textit{region}'
\end{align*}
%
To save space in the equations of Figure~\ref{fig:equations}, we use abbreviations
\term{refl}, \term{fwd}, \term{bwd}, and \term{cen} for \term{reflexive},
\term{forward}, \term{backward}, and \term{centered} regions
respectively. Futhermore, the abbreviations include syntactic sugar
for quantifying over the abseence or presence of the \irrefl{}
attribute on region constants as a boolean. For example,
the syntactic sugar for \term{fwd} is defined:
%%
\begin{align*}
\hspace{-0.25em}
& \stenFwdSR{n}{d}{r}
\; := \; \\[-0.4em]
& \qquad \begin{cases}
\stenFwd{n}{d}{, \irrefl} & \;\;\textit{if} \;\, \neg \, r \\
\stenFwd{n}{d}{}  & \;\;\textit{if} \;\,  r
\end{cases} \\
\textit{or} \;\;
& \stenFwdS{n}{d} := \stenFwd{n}{d}{}
\end{align*}
%
and similarly for \term{bwd} and \term{cen}.
We also frequently abbreviate \irrefl{} to \irreflS{}.

@@

\paragraph{Overlapping regions with +}
The first nine
equations (with labels of the form $\ldots \texttt{+} \ldots$)
explain the notion of \emph{overlapping} regions with sum
\term{+}. Note that in the first six, $r$ and $s$ range
over booleans denoting the absence (true) or presence (false)
of \irrefl{}. These are combined via disjunction. For example,
the rule $(\textsc{B} \, \term{+} \,
\textsc{F})$ explains that the addition of \term{backward}
and \term{forward} regions in the same dimension and the same
depth is equivalent to a \term{centered} region of that depth.
If the \term{forward} part is irrefleixve (\ie{}, $r =
\textit{false}$) but \term{backward} is not (\ie{}, $s =
\textit{true}$) then their addition is equal to a \term{centered}
region with no \irrefl{} modifier by the disjunction ($r \vee s =
\textit{true}$), \ie{}:
%%
\begin{align*}
& \stenCenS{n}{d}  \\[-0.2em]
\equiv \;\; & \stenFwdSR{n}{d}{\irreflS} \; \texttt{+} \; \stenBwdS{n}{d}
\end{align*}
%%
That is, the \term{fwd} region is irreflexive describing code which is missing
a zero-offset neighbourhood index (\eg{}, missing $\texttt{a(i)}$), but the addition of
the \term{bwd} has no irreflexive attribute and thus provides the
missing zero offset index.

The equation (\textsc{irrefl}) explains an annihilation of
\irrefl{} using a further syntactic sugar.
We write $R^{\irreflS}$ to denote a region constant with an
irreflexive attribute, \eg{},
%%
\begin{align*}
\stenFwdS{n}{d}^{\irreflS} \, := \,
\stenFwdSR{n}{d}{\irreflS}
\end{align*}
%%
Thus, (\textsc{irrefl}) explains the sum of a
product of two regions $R$ and $S$ with itself,
where in each component of the sum one of $R$
or $S$ has the irreflexive attribute. These cancel to give
just the specification $R \, \term{*} \, S$.

@@

\begin{figure}[t]
\begin{align*}
\begin{array}{c}
\dfrac{}{S <: S}(\textsc{refl}) \qquad \dfrac{R <: S \quad S <: T}{R <:
  T}(\textsc{trans}) \\[1.5em]
\dfrac{}{\texttt{readOnce} \, S <: S}(\textsc{rep})
\\[1.5em]
\setlength{\arraycolsep}{0.1em}
\dfrac{\hspace{3em} m \leq n \hspace{3em}}
{\begin{array}{rl}
\stenFwdS{m}{d} & <: \stenFwdS{n}{d}
%& \;\, ds \subseteq es \wedge n \leq m
\\
\wedge \stenBwdS{m}{d} & <: \stenBwdS{n}{d}
%& \;\, ds \subseteq es \wedge n \leq m
\\
\wedge \; \stenCenS{m}{d} & <: \stenCenS{n}{d}
%& \;\, ds \subseteq es \wedge n \leq m
\\
\wedge \; \stenBwdS{m}{d} & <: \stenCenS{n}{d} \\
\wedge \; \stenFwdS{m}{d} & <: \stenCenS{n}{d} \\[1em]
\end{array}} \\[2.5em]
\hspace{-0.5em}
\dfrac{S_1 <: T_1 \quad S_2 <: T_2}
      {S_1 \, \texttt{+} \, S_2 <: T_1 \, \texttt{+} \, T_2}
(\textsc{cong}\texttt{+}) \;\;\;
\dfrac{S_1 <: T_1 \quad S_2 <: T_2}
      {S_1 \, \texttt{*} \, S_2 <: T_1 \, \texttt{*} \, T_2}
(\textsc{cong}\texttt{*})
\end{array}
\end{align*}
\caption{Inequations on regions}
\label{fig:inequations}
\end{figure}

@@

Given the model defined in this section we can
consider soundness for the equational theory of
specifications and the notion of spatial approximation
on specifications. The proofs are given in our supplement.

\begin{theorem}[Soundness of equational theory]
\[
\overline{\texttt{v} : S}\equiv \overline{\texttt{u} : T}
\; \Rightarrow \;
\interp{\overline{\texttt{v} : S}} = \interp{\overline{\texttt{u} : T}}
\]
\end{theorem}

\begin{theorem}[Soundness of approximations]
\[
\overline{\texttt{v} : S} <: \overline{\texttt{u} : T}
\; \Rightarrow \;
\interp{\overline{\texttt{v} : S}} \subseteq \interp{\overline{\texttt{u} : T}}
\]
\end{theorem}

@@

\newcommand{\bplus}{\operatornamewithlimits{\term{+}}}
\newcommand{\tySum}[1]{#1^{\term{+}}}
\newcommand{\tyProd}[1]{#1^{\term{*}}}
\newcommand{\specDNF}{\textbf{spec}}
\newcommand{\result}[1]{\lfloor{#1}\rceil}

Next, the set of spans $\spanOp(M)$ covering the indexing
space is converted into abstract syntax trees
for the specification language. This conversion is defined in terms
of an algebra on \textit{spec} syntax in disjunctive-normal form
(which we denote \specDNF{}).

\begin{align*}
\result{\specDNF{}} = \specDNF + ((\specDNF{} + 1) \times
  (\specDNF{} + 1))
\end{align*}

\begin{align*}
\result{\specDNF{}} & ::= \textsf{exact} \, \specDNF{}
\mid \textsf{bounds} ([\specDNF{}], [\specDNF{}]) \\
\end{align*}

The algebra mirrors the shape
of the region combinators for addition and multiplication,
with operators $\oplus$ and $\odot$ and a constructor for \specDNF{}:
%%
\begin{align*}
\oplus & : \specDNF \rightarrow \specDNF \rightarrow
  \specDNF \\
\odot & : \specDNF \rightarrow \specDNF \rightarrow
        \specDNF \\
\mathsf{toSpec} & : (\mathbb{Z} \cup \{\infty\}) \rightarrow (\mathbb{Z} \cup
  \{\infty\})  \rightarrow \specDNF
\end{align*}
%%
The $\mathsf{toSpec}$ operation takes a pair of lower and upper bounds
values (one-dimensional) and constructs a specification
which contains a one-dimensional region.
An entire span is converted into an $n$-dimensional
specification by applying $\mathsf{toSpec}$ to each
pair of lower and upper bounds in a span, per dimension, and multiplying these
specifications by $\odot$. The resulting specifications for
each span are then summed by $\oplus$:
\begin{equation*}
\textsf{spec}(M) =
\sum\limits_{\vect{x} \in \spanOp(M)}
\prod\limits_{i \in \{1, \ldots, n\}} \, \mathsf{toSpec}(\vect{x}^L_i, \vect{x}^U_i)
\end{equation*}
(where $\oplus$ is the additive and $\odot$ is the multiplicative used
within $\Sigma$ and $\Pi$ respectively here).
We unpack the definitions of this algebra.

\begin{definition}[Specifications in DNF]
Let $r_1, ..., r_n$ range over elements of the \textit{region}
syntax (see Figure~\ref{fig:syntax}, p.~\pageref{fig:syntax}).
The set \specDNF{} is a subset of syntax trees \textit{spec}
of specifications in disjunctive normal form over regions
where the disjunct is \term{+} (since its model is in terms of set
union) and the conjunct is \term{*} (since its model is a form of tensor).
That is elements of \specDNF{} are of the form:
%%
\[
(r^1_{1} \; \term{*} \ldots \term{*} \; r^1_n)\; \term{+} \; \ldots
\term{+} \; (r^m_1 \, \term{*} \; \ldots \term{*} \; r^m_p)
\]
%%
More formally, $\specDNF \subseteq \textit{spec}$, defined:
%%
\begin{align*}
\specDNF{} & ::= [\textit{mult},] \;
\tySum{\specDNF} \\
\tySum{\specDNF} & ::= \tyProd{\specDNF} \; \term{+} \; \tySum{\specDNF} \mid
  \tyProd{\specDNF} \\
\tyProd{\specDNF} & ::= \textit{region} \; \term{*} \; \tyProd{\specDNF} \mid
   \textit{region}
\end{align*}
%%
We include the empty element $\epsilon$ which is not present in the
syntax.
In the following, $s, t$ range over elements of
\specDNF{}, $\tySum{s}, \tySum{t}$ range over elements of
$\tySum{\specDNF}$ and $\tyProd{s}, \tyProd{t}$ range over elements
of $\tyProd{\specDNF}$ (for example, $\tyProd{s} = r^1_{1} \; \term{*}
\ldots \term{*} \; r^1_n$).
\end{definition}

\begin{definition} The $\mathsf{toSpec}$ constructor is defined:
%%
%\newcommand{\llower}{\vect{x}^L_i}
%\newcommand{\lupper}{\vect{x}^U_i}
\newcommand{\llower}{l}
\newcommand{\lupper}{u}
\begin{align*}
&\mathsf{toSpec} \; \llower \; \lupper = \\
&\begin{cases}
%% FWD
 \stenFwdS{\lupper}{i}  & \llower = 0 \, \wedge \, \lupper > 0 \\[0.2em]
 \stenFwdSR{\lupper}{i}{\irreflS}  & \llower = 1 \, \wedge \, \lupper > 0 \\[0.2em]
%% BWD
 \stenBwdS{|\llower|}{i}  & \llower < 0 \, \wedge \, \lupper = 0 \\[0.2em]
\stenBwdSR{|\llower|}{i}{\irreflS} & \llower < 0 \, \wedge \, \lupper = -1 \\[0.2em]
%% CEN
 \stenCenS{\lupper}{i}  & \llower < 0 \, \wedge \, \lupper > 0
 \, \wedge \, |\llower| = \lupper \\[0.2em]
 \stenBwdS{|\llower|}{i} & \llower < 0 \, \wedge \, \lupper > 0  \, \wedge \, |\llower| \neq \lupper \\
\quad \texttt{+} \, \stenFwdS{\lupper}{i}  & \qquad\quad \\[0.2em]
% BOUND
 \texttt{atMost}, \stenFwdS{\lupper}{i} & \llower > 1 \\[0.2em]
 \texttt{atMost}, \stenBwdS{|\llower|}{i} \quad & \llower < (-1)
 \\[0.2em]
% ABSOLUTE REP
 \epsilon & \llower = \infty \, \vee \, \lupper = \infty
  \end{cases}
\end{align*}
%%
The first two cases map to \texttt{forward} stencils since the lower
bound is $0$ or $1$, with the depth determined by the upper bound of
the span. If the lower bound is $1$, then the
$0$-offset point is missing so the region is given an
\texttt{irreflexive} attribute. The second two cases are similar for
\texttt{backward} but now the depth of the region is determined by the
absolute of the lower bound. In the fifth-case, where the lower bound
is negative and the upper bound is positive and they have the same
magnitude, then a \texttt{centered} region is constructed with
the depth as the common magnitude. If the magnitudes are not the same
(sixth case) then separated \texttt{forward} and \texttt{backward}
regions are summed, with their corresponding depths.

>>>>

Figure~\ref{fig:equations} lists the equational theory for
specifications which is defined by the binary relation $\equiv$
between region terms. Stencil declarations are considered
equal when they have the same modifiers and $\equiv$ equates
their regions, \ie{}:
\begin{align*}
(\textit{region} \equiv \textit{region'}) 
 \Rightarrow \quad\;\; & \texttt{stencil} \; [\textit{approx},] \; [\textit{mult},] \;
\textit{region} \\[-0.4em]
\quad \equiv \; & \texttt{stencil} \; [\textit{approx},] \;
            [\textit{mult},] \; \textit{region}'
\end{align*}
%
The equations of Figure~\ref{fig:equations} use abbreviations
\term{refl}, \term{fwd}, \term{bwd}, \term{cen}, and \irreflS{}
for \term{reflexive}, \term{forward}, \term{backward},
\term{centered}, and \irrefl{} respectively. Futhermore, the abbreviations include syntactic sugar
for quantifying over the abseence or presence of the \irrefl{}
attribute on region constants as a boolean. For example,
the syntactic sugar for \term{fwd} is defined:
%%
\begin{align*}
\hspace{-0.25em}
& \stenFwdSR{n}{d}{r}
\; := \; \\[-0.4em]
& \qquad \begin{cases}
\stenFwd{n}{d}{, \irrefl} & \;\;\textit{if} \;\, \neg \, r \\
\stenFwd{n}{d}{}  & \;\;\textit{if} \;\,  r
\end{cases} \\
\textit{or} \;\;
& \stenFwdS{n}{d} := \stenFwd{n}{d}{}
\end{align*}
%
and similarly for \term{bwd} and \term{cen}.

@@

\paragraph{Overlapping regions with +}
The first nine
equations (with labels of the form $\ldots \texttt{+} \ldots$)
explain the notion of \emph{region overlapping} with sum
\term{+}. In the first six, $r$ and $s$ range
over booleans denoting the absence (true) or presence (false)
of \irrefl{}. These are combined via disjunction. For example,
the rule $(\textsc{B} \, \term{+} \,
\textsc{F})$ explains that the sum of \term{backward}
and \term{forward} regions in the same dimension and the same
depth is equivalent to a \term{centered} region of that depth.
If the \term{forward} part is irrefleixve ($r =
\textit{false}$) but \term{backward} is not ($s =
\textit{true}$) then their sum is equal to a \term{centered}
region with no \irreflS{} modifier by the disjunction ($r \vee s =
\textit{true}$), \ie{}:
%%
\begin{align*}
& \stenCenS{n}{d}  \\[-0.2em]
\equiv \;\; & \stenFwdSR{n}{d}{\irreflS} \; \texttt{+} \; \stenBwdS{n}{d}
\end{align*}
%%
That is, the \term{fwd} region is irreflexive describing code which is missing
a zero-offset neighbourhood index (\eg{}, missing $\texttt{a(i)}$), but the addition of
the \term{bwd} has no irreflexive attribute and thus provides the
missing zero offset index.

The equation (\textsc{irrefl}) provides an annihilation of
\irreflS{} using a further syntactic sugar.
We write $R^{\irreflS}$ to denote a region constant with an
irreflexive attribute, \eg{},
%%
\begin{align*}
\stenFwdS{n}{d}^{\irreflS}  := \,
\stenFwdSR{n}{d}{\irreflS}
\end{align*}
%%
The left-hand side of (\textsc{irrefl}) has a sum of
products of two regions $R$ and $S$, 
where in each component of the sum one of $R$
or $S$ has the irreflexive attribute. These cancel to give
just $R \, \term{*} \, S$.

@@

\begin{figure}[t]
\begin{align*}
\hspace{-0.5em}
\begin{array}{c}
%%
%% INEQUATIONS ON REGION
%% 
%\framebox{$\textit{region} <: \textit{region}'$} \\[0.85em]
%
%\dfrac{}{R <:^r R}\trule{\textsc{refl}} \qquad \dfrac{P <:^r R \quad R <:^r Q}{P <:^r
%  Q}\trule{\textsc{trans}} 
%\qquad
%\\[1.5em]
\vspace{-0.4em}
\setlength{\arraycolsep}{0.1em}
\dfrac{\hspace{3em} m \leq n \qquad\qquad r \Rightarrow s \hspace{3em}}
{\begin{array}{rl}
\stenFwdSR{m}{d}{r} & <:^r \stenFwdSR{n}{d}{s}
%& \;\, ds \subseteq es \wedge n \leq m
\\
\wedge \; \stenBwdSR{m}{d}{r} & <:^r \stenBwdSR{n}{d}{s}
%& \;\, ds \subseteq es \wedge n \leq m
\\
\wedge \; \stenCenSR{m}{d}{r} & <:^r \stenCenSR{n}{d}{s}
%& \;\, ds \subseteq es \wedge n \leq m
\\
\wedge \; \stenBwdSR{m}{d}{r} & <:^r \stenCenSR{n}{d}{s} \\
\wedge \; \stenFwdSR{m}{d}{r} & <:^r \stenCenSR{n}{d}{s} \\[1.2em]
\end{array}}\trule{\textsc{over}} \\
\hspace{-0.5em}
\dfrac{P_1 <:^r R_1 \quad P_2 <:^r R_2}
      {P_1 \, \texttt{+} \, P_2 <:^r R_1 \, \texttt{+} \, R_2}
\trule{\textsc{cong}\texttt{+}} \;\;\;
\dfrac{P_1 <:^r R_1 \quad P_2 <:^r R_2}
      {P_1 \, \texttt{*} \, P_2 <:^r R_1 \, \texttt{*} \, R_2}
\trule{\textsc{cong}\texttt{*}} \\[1.5em]
%%
%% INEQUATIONS ON SPEC
%%
%\framebox{$\textit{spec} <: \textit{spec}'$} \\[0.8em]
%
\dfrac{}{\term{readOnce} \, R <: R}\trule{\textsc{rep}}
\quad
\dfrac{}{\term{atLeast} \, R <: \term{atMost} \,
  R}\trule{\textsc{bound}} \\[1.5em]
%%
\dfrac{P <:^r R}{\term{atLeast}  P <: \term{atLeast} 
  R}\trule{\textsc{cong}\texttt{L}}
\ 
\dfrac{P <:^r R}{\term{atMost}  P <: \term{atMost} 
  R}\trule{\textsc{cong}\texttt{M}} \\[1.5em]
\dfrac{P <:^r R}{\term{readOnce} \, P <: \term{readOnce} \,
  R}\trule{\textsc{cong}\texttt{R}} 
\quad
\dfrac{R \equiv S}{R <:^r S}\trule{\textsc{eq}} 
%%
\end{array}
\end{align*}
\caption{Inequations $<:^r$ on \textit{regions} and
$<:$ on \textit{specs} (omitting reflexivity
and transitivity). }
\label{fig:inequations}
\label{-0.5em}
\end{figure}

@@

Given the model defined in this section we can
consider soundness for the equational theory of
specifications and the notion of spatial approximation. The proofs are given in our supplement.

\begin{theorem}[Soundness of equational theory (Figure~\ref{fig:equations})]
\[
S \equiv T \; \Rightarrow \;
\interp{S}_n = \interp{T}_n
\]
\end{theorem}

\begin{theorem}[Soundness of inequations
  (Figure~\ref{fig:inequations})]

Let $\leq$ be an ordering on
$\textsf{Mult}(\textsf{Approx}(\mathcal{P}(\domainVal{}^n)))$
and $\leq'$ be an ordering on
$\textsf{Approx}(\mathcal{P}(\domainVal{}^n))$ defined by the
following caluses
\begin{align*}
(M \leq' N \Rightarrow \textit{inj} \, M \leq \textit{inj} \, N) &
\qquad 
(\textsf{once} \, M \leq' \textsf{mult} \, M) \\
%%
%%
(M \subseteq N \Rightarrow \textit{inj}' M \leq' \textit{inj}' N)
& \;\;\; (\textsf{exact} M \leq  \textsf{lower} M)
\;\;\; (\textsf{lower} M \leq  \textsf{upper} M)
\end{align*}
%%
where $\textit{inj}$ ranges over the unary injections
of $\textsf{Approx}$ and $\textit{inj}'$ ranges over the injections of
$\textsf{Mult}$. Then, soundness of $<:$ is that:
%%
\[
S <: T
\; \Rightarrow \;
\interp{S}_n \leq \interp{T}_n
\]
\end{theorem}

@@

\newcommand{\bplus}{\operatornamewithlimits{\term{\huge{+}}}}
\newcommand{\tySum}[1]{#1^{\term{+}}}
\newcommand{\tyProd}[1]{#1^{\term{*}}}
\newcommand{\specDNF}{\textbf{spec}}

Next, the set of spans $\spanOp(M)$ covering the indexing
space is converted into abstract syntax trees 
of the specification language. This conversion is defined in terms
of an algebra on \textit{spec} syntax in disjunctive-normal form
(which we denote \specDNF{}), and which is wrapped
with the $\textsf{Approx}$ type (see
Definition~\ref{def:mult-and-approx},
p.~\pageref{def:mult-and-approx}), which we write as $\mathsf{A}$
for brevity.  The algebra mirrors the shape
of the region combinators for addition and multiplication, 
with operators $\oplus$ and $\odot$ and a constructor for \specDNF{}:
%%
\begin{align*}
\oplus & : \mathsf{A}(\specDNF) \rightarrow \mathsf{A}(\specDNF) \rightarrow
  \mathsf{A}(\specDNF) \\
\odot & : \mathsf{A}(\specDNF) \rightarrow \mathsf{A}(\specDNF) \rightarrow
        \mathsf{A}(\specDNF) \\
\mathsf{toSpec} & : (\mathbb{Z} \cup \{\infty\}) \rightarrow (\mathbb{Z} \cup
  \{\infty\})  \rightarrow \mathsf{A}(\specDNF)
\end{align*}
%%
The $\mathsf{toSpec}$ operation takes a pair of lower and upper bounds
values (one-dimensional) and constructs a specification 
which contains a one-dimensional region. 
An entire span is converted into an $n$-dimensional
specification by applying $\mathsf{toSpec}$ to each
pair of lower and upper bounds in a span, per dimension, and multiplying these
specifications by $\odot$. The resulting specifications for
each span are then summed by $\oplus$:
\begin{equation*}
\textsf{spec}(M) = 
\sum\limits_{\vect{x} \in \spanOp(M)}
\prod\limits_{i \in \{1, \ldots, n\}} \, \mathsf{toSpec}(\vect{x}^L_i, \vect{x}^U_i)
\end{equation*}
(where $\oplus$ is the additive and $\odot$ is the multiplicative used
within $\Sigma$ and $\Pi$ respectively here).
We unpack the definitions of this algebra.

\begin{definition}[Specifications in DNF]
Let $r_1, ..., r_n$ range over elements of the \textit{region}
syntax (see Figure~\ref{fig:syntax}, p.~\pageref{fig:syntax}).
The set \specDNF{} is a subset of syntax trees \textit{spec}
of specifications in disjunctive normal form over regions 
where the disjunct is \term{+} (since its model is in terms of set
union) and the conjunct is \term{*} (since its model is a form of tensor).
That is elements of \specDNF{} are of the form:
%%
\[
(r^1_{1} \; \term{*} \ldots \term{*} \; r^1_n)\; \term{+} \; \ldots 
\term{+} \; (r^m_1 \, \term{*} \; \ldots \term{*} \; r^m_p)
\]
%%
More formally, $\specDNF \subseteq (\textit{spec} \cup \{\epsilon\})$, defined:
%%
\begin{align*}
\specDNF{} & ::= \tySum{\specDNF} \mid \epsilon \\
\tySum{\specDNF} & ::= \tyProd{\specDNF} \; \term{+} \; \tySum{\specDNF} \mid
  \tyProd{\specDNF} \\
\tyProd{\specDNF} & ::= \textit{region} \; \term{*} \; \tyProd{\specDNF} \mid
   \textit{region}
\end{align*}
%%
We include the empty element $\epsilon$ which is not present in the
syntax. 
In the following, $s, t$ range over elements of
\specDNF{}, $\tySum{s}, \tySum{t}$ range over elements of 
$\tySum{\specDNF}$ and $\tyProd{s}, \tyProd{t}$ range over elements
of $\tyProd{\specDNF}$ (for example, $\tyProd{s} = r^1_{1} \; \term{*}
\ldots \term{*} \; r^1_n$).
\end{definition}

\newcommand{\exactR}{\mathsf{exact}\;}
\newcommand{\exact}[1]{\exactR(#1)}
\newcommand{\upperB}[1]{\mathsf{upper}\;(#1)}

\begin{definition} The $\mathsf{toSpec}$ constructor is defined:
%%
%\newcommand{\llower}{\vect{x}^L_i}
%\newcommand{\lupper}{\vect{x}^U_i}
\newcommand{\llower}{l}
\newcommand{\lupper}{u}
\begin{align*}
&\mathsf{toSpec} \; \llower \; \lupper = \\
&\hspace{-0.4em}\begin{cases}
%% FWD
\exact{\stenFwdS{\lupper}{i}}  & \llower = 0 \, \wedge \, \lupper > 0 \\[0.2em]
\exact{\stenFwdSR{\lupper}{i}{\irreflS}}\!\!\!\! & \llower = 1 \, \wedge \, \lupper > 0 \\[0.2em]
%% BWD
\exact{\stenBwdS{|\llower|}{i}}  & \llower < 0 \, \wedge \, \lupper = 0 \\[0.2em]
\exact{\stenBwdSR{|\llower|}{i}{\irreflS}}\!\!\!\! & \llower < 0 \, \wedge \, \lupper = -1 \\[0.2em]
%% CEN
\exact{\stenCenS{\lupper}{i}}& \llower < 0 \wedge \lupper > 0 \wedge |\llower| = \lupper \\[0.2em]
\exactR(\stenBwdS{|\llower|}{i} & \llower < 0 \wedge \lupper > 0  \wedge |\llower| \neq \lupper \\
\qquad\qquad \texttt{+} \, \stenFwdS{\lupper}{i}) & \\[0.2em]
% BOUND
\upperB{\stenFwdS{\lupper}{i}} & \llower > 1 \\[0.2em]
\upperB{\stenBwdS{|\llower|}{i}} \quad & \llower < (-1)
 \\[0.2em]
% ABSOLUTE REP
\exact{\epsilon} & \llower = \infty \, \vee \, \lupper = \infty
  \end{cases}
\end{align*}
%%
The first two cases map to \texttt{forward} stencils since the lower
bound is $0$ or $1$, with the depth determined by the upper bound of
the span. If the lower bound is $1$, then the
$0$-offset point is missing so the region is given an
\texttt{irreflexive} attribute. The second two cases are similar for
\texttt{backward} but now the depth of the region is determined by the
absolute of the lower bound. In the fifth-case, where the lower bound
is negative and the upper bound is positive and they have the same
magnitude, then a \texttt{centered} region is constructed with
the depth as the common magnitude. If the magnitudes are not the same
(sixth case) then separated \texttt{forward} and \texttt{backward}
regions are summed, with their corresponding depths.
